### 2019-09-03 README.Rmd
. -> ,
add vis example to README

@@

**Brenning**, A.. 2012. “Spatial Cross-Validation and Bootstrap for the Assessment of
Prediction Rules in Remote Sensing: The R Package Sperrorest.” In *2012
IEEE International Geoscience and Remote Sensing Symposium*, 5372–5.
<https://doi.org/10.1109/IGARSS.2012.6352393>.

>>>>

The following example shows the resampling method `"spcv-coords"`.

Visualization of all partitions

```{r spcv-coords-all-partitions}
library(mlr3)
library(mlr3spatiotemporal)
task <- tsk("ecuador")
resampling = rsmp("spcv-coords")
resampling$param_set$values = list(folds = 5)
resampling$instantiate(task)

autoplot(resampling, task)
```

Visualization of the first fold only

```{r spcv-coords-fold}
autoplot(resampling, task, fold_id = 1)
```

@@

**Brenning**, A., 2012. “Spatial Cross-Validation and Bootstrap for the Assessment of
Prediction Rules in Remote Sensing: The R Package Sperrorest.” In *2012
IEEE International Geoscience and Remote Sensing Symposium*, 5372–5.
<https://doi.org/10.1109/IGARSS.2012.6352393>.
